Stochastic Blockmodels for Relational Event Data

### 2012-05-29 docs/submission.tex
Add matrix plots and caption.

\begin{figure}[t]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics[scale=.5]{../figs/eckmann-small/example-obs-stats}
%\caption{Observed counts}
\end{subfigure}
\qquad
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics[scale=.5]{../figs/eckmann-small/example-estimates}
%\caption{Samples of $\beta_{p,k,l}$}
\end{subfigure}

%\fbox{\rule[.5cm]{0cm}{5cm} \rule[.5cm]{5cm}{0cm}}
\caption{%Observed counts versus model estimates from Eckmann email data.
 Left: Observed statistics across all dyadic email interactions from members of group 1 to group 3 (178 total events in total) and from members of group 3 to group 1 (179 events in total).  Right: Posterior samples of the corresponding $\beta_{p,1,3}$ and $\beta_{p,3,1}$.  In addition to finding differences in mean activity for these dyads, the model learns that events from 3 to 1 have a higher propensity for \texttt{ab-by} transitions.}
\label{fig:posteriorparams}
\end{figure}

@@

Figure \ref{fig:posteriorparams} shows examples of model estimates from data sets of dyadic interactions for the Eckmann data. Panels contain posterior credible intervals for parameters pertaining to dyads belonging to a particular block.  For example, events among nodes in cluster 1 have an increased propensity for reciprocal events -- after node A sends to node B, an event from B to A has an intensity that is $e^4$ larger, all else held constant.  Interestingly, degree effects seem to vary by block: in block (2,2) active senders are more likely to be a sender whereas in block (1,1) the number of previous occurrences for a given dyad has a larger multiplicative effect.

>>>>

\begin{figure}[t]
\centering
\begin{subfigure}[b]{0.45\textwidth}
\centering
\includegraphics[scale=.5]{../figs/eckmann-small/example-obs-stats}
%\caption{Observed counts}
\end{subfigure}
\qquad
\begin{subfigure}[b]{0.45\textwidth}
\centering
\includegraphics[scale=.5]{../figs/eckmann-small/example-estimates}
%\caption{Samples of $\beta_{p,k,l}$}
\end{subfigure}

\caption{%Observed counts versus model estimates from Eckmann email data.
 Left: Observed statistics across all dyadic email interactions from members of group 1 to group 3 (178 total events in total) and from members of group 3 to group 1 (179 events in total).  Right: Posterior samples of the corresponding $\beta_{p,1,3}$ and $\beta_{p,3,1}$.  In addition to finding differences in mean activity for these dyads, the model learns that events from 3 to 1 have a higher propensity for \texttt{ab-by} transitions.}
\label{fig:posteriorparams}
\end{figure}

\begin{figure}[t]
\centering
\begin{subfigure}[b]{0.22\textwidth}
\centering
\includegraphics[scale=.25]{../figs/eckmann-small/parmat/observed}
\caption{Observed counts}
\end{subfigure}
~
\begin{subfigure}[b]{0.22\textwidth}
\centering
\includegraphics[scale=.25]{../figs/eckmann-small/parmat/1}
\caption{Intercept estimates}
\end{subfigure}
~
\begin{subfigure}[b]{0.22\textwidth}
\centering
\includegraphics[scale=.25]{../figs/eckmann-small/parmat/2}
\caption{\texttt{ab-ba} estimates}
\end{subfigure}
~
\begin{subfigure}[b]{0.22\textwidth}
\centering
\includegraphics[scale=.25]{../figs/eckmann-small/parmat/3}
\caption{\texttt{ab-by} estimates}
\end{subfigure}
\caption{Comparing observed counts and parameter estimates.  Darker values are larger.  Estimates are rescaled posterior means $(\hat{\beta}_{p,z_i,z_j} - \hat{\mu}_p)/\hat{\sigma}_p$ for each dyad $(i,j)$.  Learned parameters suggest heterogeneity exists in both total activity (b) as well as dynamics as seen in (c) and (d).}
\label{fig:parmats}
\end{figure}

@@

Figure \ref{fig:posteriorparams} shows examples of model estimates from data sets of dyadic interactions for the Eckmann data. Panels contain posterior credible intervals for parameters pertaining to dyads belonging to a particular block.  %For example, events among nodes in cluster 1 have an increased propensity for reciprocal events -- after node A sends to node B, an event from B to A has an intensity that is $e^4$ larger, all else held constant.  Interestingly, degree effects seem to vary by block: in block (2,2) active senders are more likely to be a sender whereas in block (1,1) the number of previous occurrences for a given dyad has a larger multiplicative effect.
